---
title: "Signing Up"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.align = 'center')
library(tidyverse)
library(leaflet)

# To Turn off Scientific Notation Use this.
options(scipen = 999)
```

Below is information on how to sign up for summer league.


>> Information here with the form/link depending on how the site renders the information


# Summer League 2021

* Dates: June __ -> Aug __   
* Location: 
    How to get there? Good question. 
* Teams:

## Where

Use the following address: 470 Dartmouth Rd NW, Winston-Salem, NC 27104

__Park:__ In the dirt lot, fields are down the hill.

```{r, out.width=6, out.height=6}

whitaker <- tibble(
  name = c("Whitaker Park"),
  lat = c(36.1047464),
  long = c(-80.2878809)
)


leaflet() %>% 
  # addTiles() %>% 
    addProviderTiles(providers$HERE.normalDay) %>%
  # addProviderTiles(providers$HERE.basicMap, CartoDB
  #   options = providerTileOptions(opacity = 0.05)) %>% 
  addMarkers(whitaker$long, 
             whitaker$lat, 
             popup = whitaker$name
             ) %>%
  setView(whitaker$long, 
          whitaker$lat, 
          zoom = 11) 


# providers <- providers
```



 

Below is what we are thinking:

1. When: Mondays, disc flies at 6pm with games finishing before 8pm.  
2. Where: Whittaker  
3. Who: You!  
4. What (do you get):   
   4a. 10 weeks of co-ed Ultimate (from early June to late August) first pull at 6pm, playing to 15 or hard cap at 8pm.  
   4b. 1 day tournament on a Saturday in late August
   4c. A short sleeve jersey with a snazzy Summer League logo 
   4d. Friends! 
6. How (much): $50

Looking forward to seeing all of you out there!
-management